---
title: "Proposal for NACo Achievement Award Analysis"
subtitle: "Scope of Work, Cost Estimate, and Timeline"
author: "Atlas Analytics"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: pdf_document
---
```{r setup, include=FALSE, warning=F, message=F, results='asis'}
library(scales)
library(pander)
library(dplyr)
library(readr)
library(here)
```

## Client Information

**Client Name:** [Client's Name]  
**Company Name:** [Company's Name]  
**Contact Person:** [Contact's Name]  
**Email:** [Contact's Email]  
**Phone:** [Contact's Phone Number]  
**Project Start Date:** [Start Date]  
**Project End Date:** [End Date]

## Project Overview

The project involves the following key activities:

1. **Web Scraping:** Extracting data from multiple websites.
2. **Database Creation:** Creating a database from the scraped data
3. **Descriptive Analysis:** Performing  descriptive analyses
4. **NLP/Statistical Analysis:** Analyzing text data to predict winners of NACO Achievement Awards

## Scope of Work

### 1. Web Scraping

- **Objective:** Extract data from multiple websites and store it in a structured format.
- **Websites:** [List the websites, if known]
- **Tools:** Python (BeautifulSoup, Scrapy, Selenium, etc.)
  - **Selenium**: For interacting with and scraping dynamic web pages.
  - **Requests**: For fetching static web pages.
  - **BeautifulSoup**: For parsing HTML and XML data.
- **Estimated Duration:** 8 hours for scraping scripts to run.
- **Deliverables:** Scraping scripts, collected data in CSV/JSON format.

### 2. Database Creation

- **Objective:** This phase focuses on building a robust database to store and manage the scraped data, ensuring it is ready for analysis.
  + **Design Database Schema**: Create a schema to structure the data appropriately.
  + **Data Cleaning and Import**: Clean the data and import it into the database.
  + **Data Integrity**: Implement normalization and relationship management to maintain data integrity.
- **Tools:** Python (Pandas), SQL, R
  - **SQLite**: For a lightweight, self-contained database.
  - **Pandas**: For data cleaning and manipulation.
- **Estimated Duration:** 20 hours (4 days)
- **Deliverables:** Structured database with imported data.

### 3. Descriptive Analysis

- **Objective:** Conduct a descriptive analysis to explore the dataset and identify key trends and patterns.
  + **Generate Descriptive Statistics**: Calculate key statistics to summarize the data.
  + **Create Visualizations**: Visualize trends over time, by category, county, and state.
  + **Summarize Findings**: Provide a summary of key insights from the data.
- **Tools:** Python (Pandas), SQL
  - **Pandas**: For data analysis and manipulation.
  - **Matplotlib/Seaborn**: For creating visualizations.
- **Estimated Duration:** 12 hours (2 days)
- **Deliverables:** Visualizations and summary report of key findings.

### 4. NLP/Statistical Analysis

- **Objective:** Utilize natural language processing (NLP) and statistical methods to predict award winners based on text data.
- **Tools:** Python (NLTK, SpaCy, Scikit-learn)
  - **Scikit-learn**: For machine learning and statistical analysis.
  - **NLTK/Spacy**: For natural language processing.
- **Estimated Duration:** 24 hours (3 days)
- **Deliverables:** Predictive model, analysis report, and prediction results.

# Cost Estimate

```{r cost_estimate, echo=FALSE}
# Write the cost estimate table to a CSV file
cost_estimate <- data.frame(
  Phase = c("Web Scraping", "Database Creation", "Descriptive Analysis", "NLP/Statistical Analysis"),
  Role = c("Junior Developer", "Senior Developer", "Senior Data Scientist", "Senior Data Scientist"),
  Estimated_Hours = c(20, 15, 20, 30),
  Hourly_Rate = c(75, 100, 120, 150),
  Estimated_Cost = c(1500, 1500, 2400, 4500)
)
write_csv(cost_estimate, here("output/cost_estimate.csv"))
```

```{r cost_estimate_table, echo=FALSE}
# Display the timeline table using pander
cost_estimate2_cols <- c("Phase", "Role", "Estimated Hours",
                         "Hourly Rate ($)", "Estimated Cost ($)")
cost_estimate2 <- cost_estimate %>%
         mutate(Hourly_Rate = dollar(Hourly_Rate),
                Estimated_Cost = dollar(Estimated_Cost)) %>%
  add_row(Phase = "Total", Role = "", 
          Estimated_Hours = sum(cost_estimate$Estimated_Hours),
          Hourly_Rate = "",
          Estimated_Cost = dollar(sum(cost_estimate$Estimated_Cost))) %>%
  `colnames<-`(cost_estimate2_cols)
pander(cost_estimate2, split.table = Inf, keep.line.breaks = TRUE,
       emphasize.rownames = FALSE,  caption = "Cost Estimate")
```


<!-- | Phase                    | Role                | Estimated Hours | Hourly Rate (\$) | Estimated Cost (\$) | -->
<!-- |--------------------------|---------------------|-----------------|-----------------|--------------------| -->
<!-- | Web Scraping             | Junior Developer    | 20              | 75              | 1,500              | -->
<!-- | Database Creation        | Senior Developer    | 15              | 100             | 1,500              | -->
<!-- | Descriptive Analysis     | Senior Data Scientist | 20           | 120             | 2,400              | -->
<!-- | NLP/Statistical Analysis | Senior Data Scientist | 30           | 150             | 4,500              | -->
<!-- | **Total**                |                     | **85**          |                 | **9,900**          | -->

### Breakdown by Phase and Role

**Web Scraping**:

- **Role**: Junior Developer
- **Tasks**: Writing and running scripts to extract data from websites. Suitable for a junior developer due to the relatively straightforward nature of the tasks involved.
- **Estimated Hours**: 20 hours
- **Hourly Rate**: $75
- **Estimated Cost**: $1,500

**Database Creation**:

- **Role**: Senior Developer
- **Tasks**: Designing and implementing the database schema, importing data, and ensuring data integrity. Requires experience in database design and management, which is ideal for a senior developer.
- **Estimated Hours**: 15 hours
- **Hourly Rate**: $100
- **Estimated Cost**: $1,500

**Descriptive Analysis**:

- **Role**: Senior Data Scientist
- **Tasks**: Performing statistical analysis and generating visualizations. Involves advanced analytical skills and knowledge of data science best practices.
- **Estimated Hours**: 20 hours
- **Hourly Rate**: $120
- **Estimated Cost**: $2,400

**NLP/Statistical Analysis**:

- **Role**: Senior Data Scientist
- **Tasks**: Conducting text analysis, feature engineering, and model training. This phase involves complex statistical and machine learning techniques, requiring a senior data scientist's expertise.
- **Estimated Hours**: 30 hours
- **Hourly Rate**: $150
- **Estimated Cost**: $4,500

### Summary of Costs

The total estimated cost for the project is **$9,900**, covering all phases from web scraping to advanced NLP and statistical analysis. Each task is allocated to a role best suited to ensure efficiency and expertise in execution.

# Timeline

```{r timeline, echo=FALSE}
# Write the timeline table to a CSV file
timeline <- data.frame(
  Phase = c("Web Scraping", "Database Creation", "Descriptive Analysis", "NLP/Statistical Analysis"),
  Start_Date = c(format(Sys.Date(), "%Y-%m-%d"), format(Sys.Date() + 6, "%Y-%m-%d"), format(Sys.Date() + 11, "%Y-%m-%d"), format(Sys.Date() + 16, "%Y-%m-%d")),
  End_Date = c(format(Sys.Date() + 5, "%Y-%m-%d"), format(Sys.Date() + 10, "%Y-%m-%d"), format(Sys.Date() + 15, "%Y-%m-%d"), format(Sys.Date() + 25, "%Y-%m-%d")),
  Duration_Days = c(5, 5, 5, 10)
)
write_csv(timeline, here("output/timeline.csv"))
```

```{r timeline_table, echo=FALSE}
# Display the timeline table using pander

timeline2_cols <- c("Phase", "Start Date", "End Date", "Duration (Days)")

timeline2 <- timeline %>%
  add_row(Phase = "", Start_Date = "",  End_Date = "",
          Duration_Days = sum(timeline$Duration_Days)) %>%
  `colnames<-`(timeline2_cols)

pander(timeline2, split.table = Inf, keep.line.breaks = TRUE,
       emphasize.rownames = FALSE,  caption = "Project Timeline")
```

<!-- | Phase                    | Start Date        | End Date          | Duration (Days) | -->
<!-- |--------------------------|-------------------|-------------------|-----------------| -->
<!-- | Web Scraping             | `r Sys.Date()`    | `r Sys.Date() + 5` | 5               | -->
<!-- | Database Creation        | `r Sys.Date() + 6` | `r Sys.Date() + 10` | 5             | -->
<!-- | Descriptive Analysis     | `r Sys.Date() + 11` | `r Sys.Date() + 15` | 5            | -->
<!-- | NLP/Statistical Analysis | `r Sys.Date() + 16` | `r Sys.Date() + 25` | 10           | -->
<!-- | **Total**                |                   |                   | **25 Days**     | -->

# Conclusion

This proposal provides a detailed plan for the software engineering project, including estimated costs and timelines for each phase. The assignment of roles ensures that each task is handled by a specialist with the appropriate skills, contributing to the project's success. We are committed to delivering a high-quality solution that meets your needs and expectations.

---

**Contact Information**

For any queries or further information, please contact:

- **Kivan Polimis**
- **Email:** kivan@analyticsbyatlas.com
- **Phone:** 713-292-6693

## Payment Terms

- **Initial Deposit:** 30% of the total cost ($2,970) before project initiation.
- **Mid-Project Payment:** 30% of the total cost ($2,970) upon completion of web scraping and database creation.
- **Final Payment:** 40% of the total cost ($3,960) upon project completion.

## Terms and Conditions

1. Any changes in project scope may incur additional costs.
2. Payment is due within 30 days of invoice receipt.
3. Confidentiality and data security will be strictly maintained throughout the project.

## Acceptance

By signing below, you agree to the terms and conditions outlined in this proposal and authorize us to proceed with the project as described.

**Client Signature:** _____________________  
**Date:** _____________________

**Authorized Representative:** _____________________  
**Date:** _____________________

This proposal includes detailed breakdowns of tasks, estimated hours, and associated costs, providing a clear understanding of what the client can expect in terms of deliverables and budget. Adjustments can be made based on client-specific requirements or negotiations.
